Response to reviewers

### 2022-06-07 paper/paper-jsdse/paper-jsdse.tex
AE's comments addressed.

Thus, we re-arrange and wrangle the data into tidy data form, with columns corresponding to individual ID, year, job number, wage in dollars, and the demographic variables. This is done using the \texttt{tidyverse} suite of packages (Wickham et al. 2019): \texttt{tidyr} (Wickham 2020) to pivot the data into long-form, with \texttt{dplyr} (Wickham et al. 2020) and \texttt{stringr} (Wickham 2019) to create new variables from the downloaded data from the database, and code levels of factors by text wrangling. The long form of the data makes it possible to do these data transformations efficiently, and it is an intermediate step towards the final target data. The code for tidying the data are demonstrated at \url{https://numbats.github.io/yowie/articles/raw-to-input-data.html} but also described in the subsequent subsections.

@@

For \texttt{sex} and \texttt{race}, we have simplified the original names provided in the raw data, \texttt{SAMPLE\_SEX\_1979} and \texttt{SAMPLE\_RACE\_78SCRN}, respectively. However, it is important to note that the use of ``sex'' is probably not correct. This information is provided by the individual, and although only has two categories, is more consistent with ``gender'' as defined in Heidari et al. (2016). When using the dataset in the classroom, the educators might include discourse on the use of terms ``sex'' and ``gender''. Particularly, measuring gender as a binary variable has the potential to fail to capture people who do not identify themselves as either male or female or create measurement error for people whose gender does not align with their sex classification. From a statistical perspective, this can make it difficult to adjust survey statistics to the population when gender is measured in different categorization in different data sources. Kennedy et al. (2020) provides a helpful discussion on these topics.

@@

The second definition is the highest grade completed that is reported in each round of the survey (provided in the refreshed data as \texttt{grade}). This value can change over time, but it should only increase. This has been included in the refreshed dataset to enable richer downstream analyses, for example, if one would like to explore how the temporal changes in education level affect the wages of individuals. Hence, different from \texttt{hgc}, this variable could be used to demonstrate longitudinal and time series analysis in the classroom. This is recorded in \texttt{new\_data\_qnames} as columns beginning with \texttt{Q3-4} and \texttt{HGC} with year as a suffix. In addition, it is also in the columns beginning with \texttt{HGCREV} reflecting revised data. We chose to use these revised values because there were fewer missing values indicating it had been more thoroughly checked. In the survey years when the revised value were not reported, i.e., in 2012, 2014, 2016, and 2018, we used the unrevised version accordingly.

@@

Our target variables for the employment are to obtain respondent's mean hourly wage (\texttt{wage}), the number of jobs (\texttt{njobs}), the total hours of work per week (\texttt{hours}) for each survey year, the year when individual starting to work (\texttt{stwork}), the length of time (years) in workforce (\texttt{yr\_wforce}), and work experience measured as the number of years worked (\texttt{exp}). As the data only reports up to 5 jobs for each respondent, the maximum number of jobs is capped at 5.

@@

For \texttt{stwork} variable, we only rename the column names from \texttt{new\_data\_qnames}. This variable is then used to calculate the next variable, \texttt{yr\_wforce} for each survey round, which is the year of survey (\texttt{year}) minus the year of individual started working (\texttt{stwork}). Finally, \texttt{exp} variable is derived from the number of weeks worked since the last interview indicated as variable started with \texttt{WKSWK} in \texttt{new\_data\_qnames}. To obtain the work experience since 1979, we calculate the cumulative value. As the measurement unit is weeks, we convert this to fractional year.

The employment and demographic variables are then joined. These data are further filtered to the cohort who participated in at least three rounds in the survey, the minimum observation recommended for longitudinal data in Singer and Willett (2003). We also opt to restrict the minimum number of observations so that the data can be used to demonstrate within-person variation when it is used to teach longitudinal data. However, it is worth noting that the original data does not restrict the number of observations for each individual, i.e., there are individuals with only one and two observations.

@@

Experience is years after entering the labor force. It represents the difference between the day an individual enters the labor force (\texttt{EMPLOYERS\_ALL\_STARTDATE\_ORIGINAL.01\textasciitilde{}Y\_XRND} in the database) relative to the date of the survey, which we call \texttt{yr\_wforce}. However, using this calculation produced numbers that do not quite match the original data.

@@

An additional criterion from Singer and Willett (2003) is to only include males aged between 14 and 17 years old in 1979. With this filtering, we obtained 0 individuals in the refreshed data compared to 888 individuals in the original data. To investigate the reason for the difference, individuals from the original and refreshed dataset were matched by id. This revealed several reasons for the disparity:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  173 individuals were more than 17 years old in 1979. Thus, it looks like the description of the original data is not quite accurate that there are people older than 17 in the subset. Our decision is to also include them in the refreshed data as the new data contains an age variable, so analysts could filter them later.
\item
  715 individuals were less than or equal to 17 years old in 1979. However, they were not captured in the refreshed data because:

  \begin{enumerate}
  \def\labelenumii{\roman{enumii}.}
  \tightlist
  \item
    35 of them completed at least 12th grade with a diploma instead of GED (\texttt{ged} variable is coded as 1). This suggests they are not dropouts, and so we excluded them from the refreshed data.
  \item
    The information about \texttt{ged} is missing in 341 individuals. We decided to include them in the refreshed data.
  \item
    3 individuals have both diploma and GED (\texttt{ged} is coded as 3). These were kept in the refreshed data.
  \item
    12 individuals do not exist in \texttt{wages} data because they have participated in less than 3 rounds of the survey.
  \end{enumerate}
\end{enumerate}

The filtering was re-applied using these decisions, resulting in a refreshed dropout subset containing 865 individuals.

@@

In the original dataset, wages were inflation-adjusted to 1990 prices. This is not done for the refreshed data because we plan to keep refreshing it as the data is added to and released from the survey. Instead, we have provided a function in the R package, \texttt{yowie}, for users to conduct the inflation adjustment when they are ready to analyze the data.

>>>>

Thus, we re-arrange and wrangle the data into tidy data form, with columns corresponding to individual ID, year, job number, wage in dollars, and the demographic variables. This is done using the \texttt{tidyverse} suite of packages (Wickham et al. 2019). We use \texttt{pivot\_longer} in \texttt{tidyr} (Wickham 2020) to pivot the data into long-form. For example, we use it to pull the hourly wage (\texttt{HRPjob\_year}), which is stored in a column corresponding to each job and each year of survey, into columns: job and rate per hour. After that, \texttt{separate} from \texttt{tidyr} is also used to get the job and survey year in two separate columns. Further \texttt{dplyr} (Wickham et al. 2020) is used and \texttt{stringr} (Wickham 2019) are used to create new variables from the downloaded data from the database, and code levels of factors by text wrangling. The long form of the data makes it possible to do data transformations efficiently, and it is an intermediate step towards the final target data. The code for tidying the data are demonstrated at \url{https://numbats.github.io/yowie/articles/raw-to-input-data.html} but also described in the subsequent subsections.

@@

For \texttt{sex} and \texttt{race}, we have simplified the original names provided in the raw data, \texttt{SAMPLE\_SEX\_1979} and \texttt{SAMPLE\_RACE\_78SCRN}, respectively. However, it is important to note that the use of ``sex'' is probably not correct. This information is provided by the individual, and although it only has two categories, it is more consistent with ``gender'' as defined in Heidari et al. (2016). When using the dataset in the classroom, the educators might include discourse on the use of terms ``sex'' and ``gender''. Particularly, measuring gender as a binary variable has the potential to fail to capture people who do not identify themselves as either male or female or create measurement error for people whose gender does not align with their sex classification. From a statistical perspective, this can make it difficult to adjust survey statistics to the population when gender is measured in different categorization in different data sources. Kennedy et al. (2020) provides a helpful discussion on these topics.

@@

The second definition is the highest grade completed that is reported in each round of the survey (provided in the refreshed data as \texttt{grade}). This value can change over time, but it is non-decreasing. This has been included in the refreshed dataset to enable richer downstream analyses, for example, if one would like to explore how the temporal changes in education level affect the wages of individuals. Hence, different from \texttt{hgc}, this variable could be used to demonstrate longitudinal and time series analysis in the classroom. This is recorded in \texttt{new\_data\_qnames} as columns beginning with \texttt{Q3-4} and \texttt{HGC} with year as a suffix. In addition, it is also in the columns beginning with \texttt{HGCREV} reflecting revised data. We chose to use these revised values because there were fewer missing values indicating it had been more thoroughly checked. In the survey years when the revised value were not reported, i.e., in 2012, 2014, 2016, and 2018, we used the unrevised version accordingly.

@@

Our target for the employment-related variables is to obtain the respondent's mean hourly wage (\texttt{wage}), the number of jobs (\texttt{njobs}), the total hours of work per week (\texttt{hours}) for each survey year, the year when individual starting to work (\texttt{stwork}), the length of time (in years) in the workforce (\texttt{yr\_wforce}), and work experience measured as the number of years worked (\texttt{exp}). As the data only reports up to 5 jobs for each respondent, the maximum number of jobs is capped at 5.

@@

For the year of individual started working (\texttt{stwork}), we only rename the column names, which is \texttt{EMPLOYERS\_ALL\_STARTDATE\_ORIGINAL.01\textasciitilde{}Y\_XRND}, from \texttt{new\_data\_qnames}. This variable is then used to calculate the next variable, the length of time in the workforce (\texttt{yr\_wforce}) for each survey round, which is the year of survey (\texttt{year}) minus \texttt{stwork}. Finally, experience (\texttt{exp}) variable is derived from the number of weeks worked since the last interview indicated as variable started with \texttt{WKSWK} in \texttt{new\_data\_qnames}. To obtain the work experience since 1979, we calculate the cumulative value. As the measurement unit is weeks, we convert this to fractional year.

The employment and demographic variables are then merged into one dataset as in the original data. These data are further filtered to the cohort who participated in at least three rounds in the survey, the minimum observation recommended for longitudinal data in Singer and Willett (2003). We also opt to restrict the minimum number of observations so that the data can be used to demonstrate within-person variation when it is used to teach longitudinal data. However, it is worth noting that the original data does not restrict the number of observations for each individual, i.e., there are individuals with only one and two observations.

@@

Experience is defined as years after entering the labor force. It represents the difference between the day an individual enters the labor force (\texttt{stwork}) relative to the date of the survey, which we call \texttt{yr\_wforce}. However, using this calculation produced numbers that do not quite match the original data.

@@

An additional criterion from Singer and Willett (2003) is to only include males aged between 14 and 17 years old in 1979. With this filtering, we obtained 670 individuals in the refreshed data compared to 888 individuals in the original data. To investigate the reason for the difference, individuals from the original and refreshed dataset were matched by id. This revealed several reasons for the disparity:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  173 individuals were more than 17 years old in 1979. Thus, it looks like the description of the original data is not quite accurate that there are people older than 17 in the subset. Our decision is to also include them in the refreshed data as the new data contains an age variable, so analysts could filter them later.
\item
  79 individuals were less than or equal to 17 years old in 1979. However, they were not captured in the refreshed data because:

  \begin{enumerate}
  \def\labelenumii{\roman{enumii}.}
  \tightlist
  \item
    35 of them completed at least 12th grade with a diploma instead of GED (\texttt{ged} variable is coded as 1). This suggests they are not dropouts, and so we excluded them from the refreshed data.
  \item
    The information about \texttt{ged} is missing in 38 individuals. We decided to include them in the refreshed data.
  \item
    3 individuals have both diploma and GED (\texttt{ged} is coded as 3). These were kept in the refreshed data.
  \item
    12 individuals do not exist in \texttt{wages} data because they have participated in less than 3 rounds of the survey.
  \end{enumerate}
\end{enumerate}

The filtering was re-applied using these decisions, resulting in a refreshed dropout subset containing 863 individuals.

@@

In the original dataset, wages were inflation-adjusted to 1990 prices. This is not done for the refreshed data because we plan to keep refreshing it as the data is added to and released from the survey. Instead, we have provided a function called \texttt{adj\_inflation} in the R package, \texttt{yowie}, for users to conduct the inflation adjustment when they are ready to analyze the data.

### 2022-06-07 paper/paper.Rmd
AE's comments addressed.

Thus, we re-arrange and wrangle the data into tidy data form, with columns corresponding to individual ID, year, job number, wage in dollars, and the demographic variables. This is done using the `tidyverse` suite of packages [@tidyverse]: `tidyr` [@tidyr] to pivot the data into long-form, with `dplyr` [@dplyr] and `stringr` [@stringr] to create new variables from the downloaded data from the database, and code levels of factors by text wrangling. The long form of the data makes it possible to do these data transformations efficiently, and it is an intermediate step towards the final target data. The code for tidying the data are demonstrated at \url{`r yowie_pkgdown`/articles/raw-to-input-data.html} but also described in the subsequent subsections.

@@

For `sex` and `race`, we have simplified the original names provided in the raw data, `SAMPLE_SEX_1979` and `SAMPLE_RACE_78SCRN`, respectively. However, it is important to note that the use of "sex" is probably not correct. This information is provided by the individual, and although only has two categories, is more consistent with "gender" as defined in @SAGER. When using the dataset in the classroom, the educators might include discourse on the use of terms "sex" and "gender". Particularly, measuring gender as a binary variable has the potential to fail to capture people who do not identify themselves as either male or female or create measurement error for people whose gender does not align with their sex classification. From a statistical perspective, this can make it difficult to adjust survey statistics to the population when gender is measured in different categorization in different data sources.  @kennedy2020using provides a helpful discussion on these topics. <!--Hence, for modern societal studies, it is highly recommended to separate sex and gender in the survey question and provide more options to respond to questions on gender. -->

@@

The second definition is the highest grade completed that is reported in each round of the survey (provided in the refreshed data as `grade`). This value can change over time, but it should only increase. This has been included in the refreshed dataset to enable richer downstream analyses, for example, if one would like to explore how the temporal changes in education level affect the wages of individuals. Hence, different from `hgc`, this variable could be used to demonstrate longitudinal and time series analysis in the classroom. This is recorded in `new_data_qnames` as columns beginning with `Q3-4` and `HGC` with year as a suffix. In addition, it is also in the columns beginning with `HGCREV` reflecting revised data. We chose to use these revised values because there were fewer missing values indicating it had been more thoroughly checked. In the survey years when the revised value were not reported, i.e., in 2012, 2014, 2016, and 2018, we used the unrevised version accordingly. <!--We also check the consistency between `hgc_i` and `grade`. Some problematic observations were found, for example, `grade` value is greater than `hgc_i`. We then fix this problem by replacing those `grade` that is greater than its `hgc_i`. -->

@@

Our target variables for the employment are to obtain respondent's mean hourly wage (`wage`), the number of jobs (`njobs`), the total hours of work per week (`hours`) for each survey year, the year when individual starting to work (`stwork`), the length of time (years) in workforce (`yr_wforce`), and work experience measured as the number of years worked (`exp`). As the data only reports up to 5 jobs for each respondent, the maximum number of jobs is capped at 5.

@@

For `stwork` variable,  we only rename the column names from `new_data_qnames`. This variable is then used to calculate the next variable, `yr_wforce` for each survey round, which is the year of survey (`year`) minus the year of individual started working (`stwork`). Finally, `exp` variable is derived from the number of weeks worked since the last interview indicated as variable started with `WKSWK` in `new_data_qnames`. To obtain the work experience since 1979, we calculate the cumulative value. As the measurement unit is weeks, we convert this to fractional year.

The employment and demographic variables are then joined. These data are further filtered to the cohort who participated in at least three rounds in the survey, the minimum observation recommended for longitudinal data in @SingerJudithD2003Alda. We also opt to restrict the minimum number of observations so that the data can be used to demonstrate within-person variation when it is used to teach longitudinal data. However, it is worth noting that the original data does not restrict the number of observations for each individual, i.e., there are individuals with only one and two observations.

@@

Experience is years after entering the labor force. It represents the difference between the day an individual enters the labor force (`EMPLOYERS_ALL_STARTDATE_ORIGINAL.01~Y_XRND` in the database) relative to the date of the survey, which we call `yr_wforce`. However, using this calculation produced numbers that do not quite match the original data.

@@

In the original dataset, wages were inflation-adjusted to 1990 prices. This is not done for the refreshed data because we plan to keep refreshing it as the data is added to and released from the survey. Instead, we have provided a function in the R package, `r yowie`, for users to conduct the inflation adjustment when they are ready to analyze the data.

>>>>

Thus, we re-arrange and wrangle the data into tidy data form, with columns corresponding to individual ID, year, job number, wage in dollars, and the demographic variables. This is done using the `tidyverse` suite of packages [@tidyverse]. We use `pivot_longer` in `tidyr` [@tidyr] to pivot the data into long-form. For example, we use it to pull the hourly wage (`HRPjob_year`), which is stored in a column corresponding to each job and each year of survey, into columns: job and rate per hour. After that, `separate` from `tidyr` is also used to get the job and survey year in two separate columns. Further `dplyr` [@dplyr] is used and `stringr` [@stringr] are used to create new variables from the downloaded data from the database, and code levels of factors by text wrangling. The long form of the data makes it possible to do data transformations efficiently, and it is an intermediate step towards the final target data. The code for tidying the data are demonstrated at \url{`r yowie_pkgdown`/articles/raw-to-input-data.html} but also described in the subsequent subsections.

@@

For `sex` and `race`, we have simplified the original names provided in the raw data, `SAMPLE_SEX_1979` and `SAMPLE_RACE_78SCRN`, respectively. However, it is important to note that the use of "sex" is probably not correct. This information is provided by the individual, and although it only has two categories, it is more consistent with "gender" as defined in @SAGER. When using the dataset in the classroom, the educators might include discourse on the use of terms "sex" and "gender". Particularly, measuring gender as a binary variable has the potential to fail to capture people who do not identify themselves as either male or female or create measurement error for people whose gender does not align with their sex classification. From a statistical perspective, this can make it difficult to adjust survey statistics to the population when gender is measured in different categorization in different data sources.  @kennedy2020using provides a helpful discussion on these topics. <!--Hence, for modern societal studies, it is highly recommended to separate sex and gender in the survey question and provide more options to respond to questions on gender. -->

@@

The second definition is the highest grade completed that is reported in each round of the survey (provided in the refreshed data as `grade`). This value can change over time, but it is non-decreasing. This has been included in the refreshed dataset to enable richer downstream analyses, for example, if one would like to explore how the temporal changes in education level affect the wages of individuals. Hence, different from `hgc`, this variable could be used to demonstrate longitudinal and time series analysis in the classroom. This is recorded in `new_data_qnames` as columns beginning with `Q3-4` and `HGC` with year as a suffix. In addition, it is also in the columns beginning with `HGCREV` reflecting revised data. We chose to use these revised values because there were fewer missing values indicating it had been more thoroughly checked. In the survey years when the revised value were not reported, i.e., in 2012, 2014, 2016, and 2018, we used the unrevised version accordingly. <!--We also check the consistency between `hgc_i` and `grade`. Some problematic observations were found, for example, `grade` value is greater than `hgc_i`. We then fix this problem by replacing those `grade` that is greater than its `hgc_i`. -->

@@

Our target for the employment-related variables is to obtain the respondent's mean hourly wage (`wage`), the number of jobs (`njobs`), the total hours of work per week (`hours`) for each survey year, the year when individual starting to work (`stwork`), the length of time (in years) in the workforce (`yr_wforce`), and work experience measured as the number of years worked (`exp`). As the data only reports up to 5 jobs for each respondent, the maximum number of jobs is capped at 5.

@@

For the year of individual started working (`stwork`),  we only rename the column names, which is `EMPLOYERS_ALL_STARTDATE_ORIGINAL.01~Y_XRND`, from `new_data_qnames`. This variable is then used to calculate the next variable, the length of time in the workforce (`yr_wforce`) for each survey round, which is the year of survey (`year`) minus `stwork`. Finally, experience (`exp`) variable is derived from the number of weeks worked since the last interview indicated as variable started with `WKSWK` in `new_data_qnames`. To obtain the work experience since 1979, we calculate the cumulative value. As the measurement unit is weeks, we convert this to fractional year.

The employment and demographic variables are then merged into one dataset as in the original data. These data are further filtered to the cohort who participated in at least three rounds in the survey, the minimum observation recommended for longitudinal data in @SingerJudithD2003Alda. We also opt to restrict the minimum number of observations so that the data can be used to demonstrate within-person variation when it is used to teach longitudinal data. However, it is worth noting that the original data does not restrict the number of observations for each individual, i.e., there are individuals with only one and two observations.

@@

Experience is defined as years after entering the labor force. It represents the difference between the day an individual enters the labor force (`stwork`) relative to the date of the survey, which we call `yr_wforce`. However, using this calculation produced numbers that do not quite match the original data.

@@

In the original dataset, wages were inflation-adjusted to 1990 prices. This is not done for the refreshed data because we plan to keep refreshing it as the data is added to and released from the survey. Instead, we have provided a function called `adj_inflation` in the R package, `r yowie`, for users to conduct the inflation adjustment when they are ready to analyze the data.

### 2022-06-07 paper/paper.tex
AE's comments addressed.

The highest grade completed has some confusion. There are several ways this is reported, including the highest grade ever completed and also the \texttt{hgc} at each survey year. To match the original data, it is appropriate to use the \texttt{hgc} while in high school. The documentation suggests this variable is available, but it is not actually present in the data. Hence, to match the original data, we have calculated the \texttt{hgc} to match the \texttt{hgc} achieved in the years between 1979 and 1994 based on the yearly survey value. The result does not exactly match the original for a few individuals.

In the original dataset, wages were inflation-adjusted to 1990 prices. This is not done for the refreshed data because we plan to keep refreshing it as the data is added to and released from the survey. Instead, we have provided a function in the R package, \texttt{yowie}, for users to conduct the inflation adjustment when they are ready to analyze the data.

>>>>

The reporting of highest grade completed is confusing. There are several ways this is reported, including the highest grade ever completed and also the \texttt{hgc} at each survey year. To match the original data, it is appropriate to use the \texttt{hgc} while in high school. The documentation suggests this variable is available, but it is actually not. Hence, to match the original data, we have calculated the \texttt{hgc} to match the \texttt{hgc} achieved in the years between 1979 and 1994 based on the yearly survey value. The result does not exactly match the original for a few individuals.

In the original dataset, wages were inflation-adjusted to 1990 prices. This is not done for the refreshed data because we plan to keep refreshing it as the data is added to and released from the survey. Instead, we have provided a function called \texttt{adj\_inflation} in the R package, \texttt{yowie}, for users to conduct the inflation adjustment when they are ready to analyze the data.

### 2022-06-07 response/response3.Rmd
rlm comment on Huber, ignore it
AE's comments addressed.

Thank you!

@@

Nothing to respond to here.

@@

Corrected as follows

@@

The abstract does NOT promise an exploratory analysis for longitudinal data. It mentions that one of the purposes of this textbook data is to use it to teach exploratory analysis of longitudinal data. Similarly, it also states that the data is useful for teaching modeling. Both of these are beyond the scope of this paper. They are still important to keep because it makes the reader aware of why this data is useful and important. No change to abstract was made.

@@

* Dewi to do

@@

* Dewi to do

@@

* Dewi to do

@@

* Dewi to do

@@

* Yes it is correct, the formatting of all Q... variables uses the same format as downloaded data from the database.

@@

* Dewi to do

@@

* It is assumed that people will not work more than 12 hours a day. Dewi to do.

@@

* Dewi to do

@@

@@

@@

@@

>>>>

* Thank you!

@@

* Nothing to respond to here.

@@

* Corrected as follows.

@@

* The abstract does NOT promise an exploratory analysis for longitudinal data. It mentions that one of the purposes of this textbook data is to use it to teach exploratory analysis of longitudinal data. Similarly, it also states that the data is useful for teaching modeling. Both of these are beyond the scope of this paper. They are still important to keep because it makes the reader aware of why this data is useful and important. No change to abstract was made.

@@

* It has been removed from the sentence.

@@

* Done.

@@

* This sentence has been modified.

@@

* We have modified this sentence and change the word to be non-decreasing.

@@

* Yes it is correct, the formatting of all Q... variables uses the same format as the downloaded data from the database.

@@

* We have modified this sentence.

@@

* It is assumed that people usually do not work more than 12 hours a day. Moreover, this value is more than the cut-off of upper value if we used the IQR method, which is only 67 hours.

@@

* We do not mention the `join()` function in the manuscript. It is true that we mentioned "the employment and demographic variables are then joined". However, in the current version, we have changed "join" to be "merged" so that it could reach people who are not familiar with `dplyr`.

@@

* We are really not sure what you are requesting here. The section was re-written in the revision. We don't refer to huber weighting, and it makes no sense to refer to bisquare.

@@

* We have done as you suggest for the density plots, but feel the back-to-back bar chart is better for the `hgc` comparison.

@@

* We have changed "unsatisfactorily" to "disappointingly".

@@

* This bullet list is a path forward. It is clearly not a summary of what was presented. We did not discuss teaching modeling. We simply used one type of model for pre-processing the data to handle unusual observations. No change made.
